Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2019-03-08 article.tex
EOD

Transmembrane helices (TMHs) are an overlooked source of 
major histocompatibility complex (MHC) class I epitopes.
It is unknown why this is the case and 
whether MHC-II also is an overlooked source of epitopes.
This study investigates if there is an evolutionary conservation 
of a pathogen's TMHs and if this is matches 
with MHC-II's over/equally/under-presenting TMHs.
We find that ...
\end{abstract}

>>>>

Transmembrane helices (TMHs) are an overlooked source of 
major histocompatibility complex (MHC) class I epitopes.
It is unknown why this is the case and 
whether MHC-II also is an overlooked source of epitopes.
This study investigates if there is an evolutionary conservation 
of a pathogen's TMHs and if this is matches 
with MHC-II's binding to TMHs more/less/equal as expected by chance.
We find that ...
\end{abstract}
